### 2017-04-14 Paper01_EnthalpyAndCrystallization.tex
Results - Added m figure, and labelled heated xrd figure. Moved unused figures to own directory

@@

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.95\textwidth]{XTalPath_Facet_FullStack_Smooth.png}
	\caption[Table of contents Capition]{\acrshort{xrd} pattern for \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
	\label{fig:TF_DSC_XRDHeating}
\end{figure}

>>>>

Relaxed \gls{dsc} of bulk material taken at different heating rates was used to establish the fragility of the \MgZnCa system.
$\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.972$

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.95\textwidth]{Bulk_Fitted_mValue.png}
	\caption[Table of contents Capition]{Fitted fragility for the \MgZnCa system obtained by \acrshort{dsc} at various heating rates}
	\label{fig:Bulk_Fitted_mValue}
\end{figure}

@@

%single image
\begin{figure}[b]
	\centering
	\includegraphics[width=0.95\textwidth]{XTalPath_Facet_FullStack_Smooth_Labelled_HeavyCull.png}
	\caption[Table of contents Capition]{\acrshort{xrd} pattern for \MgZnCa~ heated through several crystallization peaks identified from \acrshort{dsc}}
	\label{fig:TF_DSC_XRDHeating}
\end{figure}
